% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
\documentclass[
  11pt]{article}
\usepackage{xcolor}
\usepackage[a4paper,margin=25mm]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{DejaVu Serif}
  \setsansfont[]{DejaVu Sans}
  \setmonofont[]{DejaVu Sans Mono}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{longtable,booktabs,array}
\newcounter{none} % for unnumbered tables
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{amssymb}\usepackage[normalem]{ulem}\let\st\sout
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  colorlinks=true,
  linkcolor={black},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}

\title{Born from causality, Tsirelson from steering, and the amplitude seam}
\author{}
\date{}

\begin{document}
\maketitle

\section{Born from causality, Tsirelson from steering, and the amplitude
seam:}\label{born-from-causality-tsirelson-from-steering-and-the-amplitude-seam}

\section{an internal reconstruction inside a geometric hidden-connection
model}\label{an-internal-reconstruction-inside-a-geometric-hidden-connection-model}

\textbf{Cycle 3 draft v1.} Author: A. Oktyabrev (aoktyabrev@gmail.com).
Status: assembly draft (\textasciitilde11 pp + battery appendix). All
numbers cite raw as \texttt{file\ (commit)}. Claim-discipline per
program standard: theorem only with written proof + battery + review;
conjecture otherwise.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Abstract}\label{abstract}

Within a geometric hidden-connection (``ribbon'') model we close, and
then delimit, an internal reconstruction of quantum correlations. (i)
Where a mechanism carries \textbf{steering} --- conditional states with
internally generated diversity D(χ)\textgreater0 --- the no-signaling
prohibition forces the Born exponent p=2 uniquely; the derivation is
internal (the steering ensembles are produced by a shifted source
measure, not imported), executable, and robust under five deformations
of the measure. (ii) Mechanisms that resolve outcomes \textbf{locally}
are capped by Bell's theorem at S=2, with a \textbf{1/3-cosine point}
(E=cosθ/3) as their isotropic-cosine ceiling, anchored analytically and
reached by two mechanisms, with ISO-DYN bracketing it. (iii) The
\textbf{amplitude seam} between that ceiling and the quantum value S=2√2
is not crossed by decorating local mechanisms --- three registered
attempts fail on a trilemma of horns (no steering / no amplitude /
superluminal telegraph) --- but only by \textbf{joint, nonlocal
resolution}, which by our foliation results demands a shared,
statistically invisible precedence structure --- a preferred foliation
being one realization, a frameless shared order-coin another (class-M
theorem). The bridge statement is an exact division of labor, not a
unification.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{1. Introduction --- the import and the
question}\label{introduction-the-import-and-the-question}

The program's canonical text acknowledged an \textbf{import}: partially
entangled ensembles were introduced by hand (``within this
ansatz\ldots{} we make no claim of a general derivation of the Born
rule'', FINAL\_v1:284--290). Cycle 3 asks whether the steering that
underlies the Born rule can be \textbf{generated internally} by the
model's own geometry, and --- once it is --- what exactly stands between
such a mechanism and full quantum correlations. The answer assembles
into four registered statements (RULE, CEILING, SEAM, FRAME), each with
kill-criteria and public commits.

\subsection{2. Method frame}\label{method-frame}

This work is preregistered. Each campaign registers predictions,
estimators, and \textbf{kill criteria} (owned by the operator)
\emph{before} raw data; the pipeline is raw → commit → analysis, with
executable prereg↔JSON assert checklists run before every battery.
Batteries are pure numpy (N=2·10⁶ unless noted), PRNGKey from config;
analytics sit beside numerics (a \textgreater2σ mismatch is a stop).
Claim-discipline: \textbf{theorem} only with a written proof, a battery,
and operator review; \textbf{conjecture} otherwise.

\textbf{Reproduction.} The full numpy battery suite of cycle 3
reproduces bitwise: re-executed with fixed seeds, every results JSON is
byte-identical under \texttt{git\ diff} (C3-B B1--B7, hardening, L3, L1,
L2, C3-S, β-coin), and C3-B and the β-coin were independently reproduced
by the operator in a separate environment.

\textbf{Self-correction register (a feature, not dirty laundry).} Every
false stop and retraction below was caught by a preregistered criterion
or a literature check, not by hindsight; all are public with commits.

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\#
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
What
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Caught by
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Resolution
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Commit
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
1 & Δ(2)\textgreater0 (normalized conditional axis broke total
probability) & ``Δ(2)\textgreater0 = bug'' criterion & raw sub-unit
Bloch vector & 968aaa5 \\
2 & Quadrature-tolerance gate (absent from prereg) false-stopped T1/T2 &
prereg↔registered criterion & \textless2σ criterion + algebraic zero at
p=2; no threshold loosened & ccf5af6 \\
3 & Monte-Carlo cross-range would false-stop the foliation test &
control design & common-random-number comparison & 49e8c1b \\
4 & §2.3 over-claim (``no-signaling alone bounds Tsirelson'') & battery
rediscovered the PR-box fact {[}PR94{]} & narrowed to steering-endowed
layers & 2053106 \\
5 & Frame over-claim (``preferred frame required'') & class-M theorem
T3′ + β-coin & ``shared statistically invisible precedence structure'';
foliation one realization & c8e1bf3 \\
\end{longtable}
}

Section 8 gives the detailed methods and controls; this frame is the
summary a reader needs first.

\subsection{3. Model}\label{model}

\textbf{Source / steering (F2).} A shared connection orientation λ on S²
is drawn from a shifted measure μ\_χ ∝ 1+χλ\_z. A measurement setting a
partitions λ by s=sign(λ·a); the conditional ensemble's \textbf{raw}
(sub-unit) mean vector m\_s is the steered state; readout probability
f\_p(c)=\textbar1+c\textbar{}\textsuperscript{\{p/2\}/(\textbar1+c\textbar{}}\{p/2\}+\textbar1−c\textbar\^{}\{p/2\}),
with f\_∞ the step 1\{c\textgreater0\}. \textbf{Lesson (record):}
normalizing the conditional axis broke total probability and produced
Δ(p=2)\textgreater0 --- the ``Δ(2)\textgreater0 = bug'' criterion caught
it; the raw sub-unit Bloch vector is correct (battery\_c3b, 968aaa5).

\textbf{Joint / chord layer.} A postulated pair law
P(s,t\textbar a,b)=(1−st cosθ)/4 (E=−cosθ, S\_max=2√2), and its weighted
generalization \textbar s√w\_a a − t√w\_b b\textbar\^{}p, used where the
mechanism resolves the pair jointly rather than by local readout of λ.

\subsection{4. RULE --- Born from no-signaling, internally
(C3-B)}\label{rule-born-from-no-signaling-internally-c3-b}

\textbf{Steering is generated, not imported.} With μ\_χ, χ\textgreater0
yields steering diversity D(χ): 0.03→0.08 as χ grows
(C3B\_hardening.json, 968aaa5) --- remote ensembles with \textbf{equal
means, distinct higher moments}.

\textbf{Selection lemma (executable).} For the readout as a random
variable over the conditioning, no-signaling ⇔ the readout is affine in
the projection (Jensen gap of an affine map ≡ 0). Affinity ∩ oddness
(f(−c)=1−f(c)) ∩ normalization = the single rule f₂=(1+c)/2 ⇒
\textbf{p=2 uniquely}. The algebraic zero at p=2 is exact (addendum2,
ccf5af6); the non-affine tail is strictly positive --- scan Δ(4)=0.042,
Δ(6)=0.105, Δ(10)=0.217, Δ(∞)=0.375, monotone, analytic↔numeric
\textless2σ (C3L\_L3.json, 9567ddb).

\textbf{Hardened to theorem.} T1 (sequential/order, B7): repeatability
1.0000, order commute, no-signaling both orders, post-measurement
null-set \{2\}. T2 (anti-circularity): \textbf{five} measure
deformations (μ\_κ, κ∈\{0.5,2,3\}; two cubic), all D\textgreater0,
analytic null-set \{2\}, \textbar analytic−numeric\textbar\textless2σ.
T3 (F1 direct law) is a boundary (postulated, not steering-collapse).
Verdict: \textbf{internal derivation of the Born rule from no-signaling
within the ribbon's steering class} (C3B\_hardening.json, c152c98). One
\textbf{false stop} en route --- a quadrature-tolerance gate absent from
preregistration --- was caught, documented, and corrected without
loosening any registered criterion (addendum2, ccf5af6; §8).

\textbf{Mechanical realization (C3-B-mech, form-free).} The steering
premise is realized mechanically and form-free: an annealed,
field-magnetized and fast-frozen elastic source supplies a polar-biased
orientation measure that fits no registered closed form; no closed form
is needed. The sign-readout conditionals of that measure carry steering
diversity in the third and fifth moments, matching the Jensen analytics
computed directly on the empirical ensembles, with the unbiased (h=0)
control showing null effects throughout; on ensembles produced entirely
by the elastic dynamics, no-signaling selects p=2. The selection
theorem's premise thus rests on measured moments, not on an assumed
measure --- a weaker assumption and hence a stronger claim
(C3Bmech\_M1M2.json, 2080bbe; M1\(\checkmark\)M2\(\checkmark\) in
form-free mode). That the source measure admits no closed form is kin to
the C2-TM wall (the relaxational amplitude A(k\_f) likewise has no
closed form): an observation --- elasticity does not favor closed forms
--- not a theorem.

\subsection{5. CEILING --- the 1/3-cosine
point}\label{ceiling-the-13-cosine-point}

Local resolution (hidden λ + local linear readout) yields
E(a,b)=E\_λ{[}(λ·a)(λ·b){]}=aᵀ(⅓I)b = \textbf{cosθ/3} (χ-corrections odd
⇒ vanish), S=2√2/3≈0.943 --- the isotropic-cosine ceiling of the local
layer. The exact convergence is analytic (lever rule, exactly 1/3) and
frame-local (E(0)=0.333; C3L\_L2.json, 49e8c1b); dynamical
isotropization lands NEAR the point: ρ\_cos=0.311±0.010 (cosine-fit, the
form-matched estimator; raw C2ISO\_analysis.json: cells/kf4.0/rho\_cos =
0.3113, a043f8f), ρ\_model-free=0.336 (same file) --- bracketing 1/3
within \textasciitilde2σ. Estimators named per program rule. Anchored
analytically and reached by two mechanisms, with ISO-DYN bracketing it ⇒
a structural boundary, the lower bank of the seam.

\subsection{6. SEAM --- the trilemma of horns
(C3-S)}\label{seam-the-trilemma-of-horns-c3-s}

Can an internal model reach \textbf{D\textgreater0 and S=2√2} together?
Registered attempts, ansätze fixed before batteries: - \textbf{S-F1}
(weighted chord, α=√(1+χ), β=√(1−χ)): S(χ)=2√2·√(1−χ²) --- reaches 2√2
only at χ=0 (symmetry), but is postulated (no continuous measure) ⇒
D\_joint N/A. \textbf{Horn: no internal steering.} - \textbf{S-F2}
(shifted source × chord/product mixture): S(χ)=√2·(1+χ/3)≤1.886, and
P(s\textbar a,λ)=½ ⇒ Alice does not update λ ⇒ D\_joint≈0. \textbf{Horn:
no amplitude / no steering} (C3S.json, 324f097). - \textbf{S-F3} (local
bias × chord kernel, \textbar·\textbar{} ansatz with κ): steers
(D\textgreater0) but the marginal carries Bob-setting dependence at
O(κχ) --- telegraph 0.500→0.542 (C3S\_F3\_check.py; analytics 2053106).
\textbf{Horn: superluminal telegraph} --- kin to finite-speed no-gos
{[}BPA12{]}.

\textbf{Reduction (Bell corollary, not a new theorem).} The internal
class = λ-average of local responses = LHV ⇒ S≤2. Closing the seam
therefore demands \textbf{joint, nonlocal resolution}; and joint
resolution demands a shared, statistically invisible precedence
structure (§7). Attempt count: 3. (C3S\_seam\_reduction.md.)

\subsection{7. FRAME --- foliation (C3-L,
L1/L2)}\label{frame-foliation-c3-l-l1l2}

On the chord joint law, two resolution mechanics: - \textbf{(i)
preferred-foliation:} S=2√2 \textbf{identical across five foliations}
(cross-disc 0.000000 under common random numbers), foliation
statistically invisible (C3L\_L2.json, 49e8c1b). - \textbf{(ii)
frame-local:} space-like → LHV ceiling S=0.943; time-like A→B, B→A →
reconstruct 2√2. L1: the joint admits an order-invariant realization
(existential PASS, factorized witness disc=0.00); the collapse
realization's order-dependence (0.0418 with invariant marginals) is
evidence for L2c, not pathology (addendum1). \textbf{Method note:} the
foliation-invariance test required common random numbers --- a raw
cross-range would false-STOP on Monte-Carlo noise (§8).

\textbf{Class-M theorem} (status: theorem; canonical statement in
\texttt{sim/cycle3/C3L\_L2c\_THEOREM.md}, c8e1bf3): in the class M of
outcome-definite sequential resolution mechanisms (shared preparation
randomness λ, setting-independence M4′, no retrocausation),
S\textgreater2 is achievable \textbf{iff} M admits a shared,
space-like-transcending, statistically invisible precedence structure.
Realizations demonstrated: a preferred foliation (five axes,
cross-discrimination 0.000000 under CRN) and a \textbf{frameless per-run
shared order-coin} (S=2√2±2σ, no telegraph, coin invisible; battery
c8e1bf3, independently re-executed). The earlier conjecture's
``preferred foliation is required'' was \textbf{retracted as too strong}
during the adversarial passes: the foliation is one realization of the
required structure, not its only form. Experimental anchor unchanged:
before-before experiments {[}ZBGT01, SZGS02{]} exclude the frame-local
branch in nature; what survives is joint resolution carrying a shared,
hidden precedence structure. Kin: Bohmian preferred slicing {[}DGZ92{]},
steering-axiomatic reconstructions {[}CDP11{]}; {[}H92{]}, {[}SS97{]}.

\subsection{8. METHODS --- batteries, controls, self-correction (detail;
summary in
§2)}\label{methods-batteries-controls-self-correction-detail-summary-in-2}

All batteries: pure numpy, N=2·10⁶, PRNGKey from config, analytics
beside numerics (\textgreater2σ mismatch = stop), assert prereg↔JSON
before raw, raw→commit→ analysis. Estimator named in every prediction;
metric = the model observable.

\textbf{Registered false stops and their resolution (part of the
evidence):} 1. \textbf{Δ(2)\textgreater0 = bug} (C3-B): normalized
conditional axis broke total probability; fixed to raw Bloch (968aaa5).
2. \textbf{Quadrature gate} (hardening): an analytic-tolerance gate
(tol=1e-9 on a 20001-pt trapezoid, error \textasciitilde2.3e-5)
false-STOPped T1/T2; corrected to the registered \textless2σ criterion +
algebraic zero at p=2; threshold \textbf{not} loosened to pass
(addendum2, ccf5af6). 3. \textbf{Monte-Carlo cross-range} (L2): raw
5-foliation range would false-STOP; replaced by common-random-number
comparison (49e8c1b). 4. \textbf{§2.3 over-claim retraction} (C3-S): the
first §2.3 asserted ``no-signaling alone cuts p\textgreater2 in the
joint layer''; J5 rediscovered the Popescu--Rohrlich fact that the
postulated \textbar·\textbar\^{}p family is no-signaling up to the PR
box {[}PR94{]}; the claim was narrowed to steering-endowed layers
(324f097; §9). 5. \textbf{Frame over-claim} (abstract/§5/§8/§9 v1):
``preferred frame required'' --- retracted by the class-M theorem's T3′
and the β-coin demonstration; revised in v2, history retained. §9
CEILING wording aligned in v2. Each was caught by a preregistered
criterion, not by hindsight.

\textbf{Reproduction.} The full numpy battery suite of cycle 3 was
independently re-executed (2026-07-21); fixed-seed raw reproduces
bitwise (C3-B B1--B7, C3-B hardening, L3, L1, L2, C3-S, β-coin --- all
results JSON byte-identical under \texttt{git\ diff}). C3-B and the
β-coin were additionally reproduced by the architect in a separate
environment.

\subsection{9. The Tsirelson section (§2.3, corrected ---
verbatim)}\label{the-tsirelson-section-2.3-corrected-verbatim}

\begin{quote}
Rule selection is exactly as strong as steering. In any layer whose
measurements produce conditional states that can themselves be steered
--- internally generated diversity D\textgreater0 --- the Jensen
argument applies: no-signaling forces affinity, selects p=2, and with it
the quantum value of S available to that layer. In a bare-correlation
joint layer, however, where outcomes carry no post-measurement
structure, the \textbar·\textbar\^{}p family has uniform marginals for
every p: the entire family is no-signaling, up to and including the PR
box --- the classic observation of Popescu and Rohrlich {[}PR94{]},
which our battery rediscovered as a registered finding against an
earlier over-claim of this section (retained in the record).
No-signaling alone therefore does not enforce the Tsirelson bound; what
enforces it, in this geometry, is no-signaling PLUS steering structure
--- and this localizes, within one construction, the same gap that
information causality {[}Paw09{]} was invented to fill. The amplitude
seam then resolves into a reduction rather than a mystery: within the
internally-generated class (hidden measure plus local response) Bell's
theorem itself caps S at 2, so closing the seam --- D\textgreater0
together with S=2√2 --- demands joint, nonlocal resolution of the pair;
and joint resolution, by the foliation results above, demands a
preferred frame that the statistics provably hide. {[}Revised by the
class-M theorem, §7: read `a shared, statistically invisible precedence
structure', of which a preferred frame is one realization --- the
frameless order-coin is another.{]} The program's bridge statement
follows: Einstein's prohibition selects the quantum rule wherever
mechanisms carry steering; the quantum amplitude is bought only by joint
resolution, whose frame Einstein's own statistics render invisible.
\end{quote}

\subsection{10. Outlook (verbatim)}\label{outlook-verbatim}

\begin{quote}
Three cycles of this program asked one question from three sides: what
stands between a mechanism and quantum correlations. The answer
assembled itself into four registered statements. (1) RULE: wherever a
mechanism carries steering --- conditional states with internally
generated diversity --- the prohibition of superluminal signaling forces
the Born exponent p=2 uniquely; the derivation is internal, executable,
and robust to deformations of the source measure. (2) CEILING:
mechanisms that resolve outcomes locally (hidden measure plus local
response) are capped by Bell's theorem at S=2, with the 1/3-cosine point
as their isotropic-cosine ceiling --- a landmark anchored analytically
(the lever rule), reached by frame-local resolution, and bracketed by
relaxational dynamics (estimator-dependent, §5). (3) SEAM: the gap
between that ceiling and the quantum value is not crossed by decorating
local mechanisms --- our registered attempts fail on a trilemma of horns
(no steering, no amplitude, or superluminal telegraph; kin to
finite-speed no-gos {[}BPA12{]}) --- it is crossed only by joint
resolution of the pair. (4) FRAME: joint resolution of the frame-local
kind reconstructs the Suarez--Scarani alternative and degrades to the
local ceiling, which real before-before experiments {[}ZBGT01, SZGS02{]}
have excluded in nature; the surviving corner, joint resolution carrying
a shared, statistically invisible precedence structure (foliation or
shared order-coin), reproduces quantum statistics exactly while
rendering its own precedence structure statistically invisible to the
resolution of our batteries. The bridge statement of the program is
therefore not a unification but an exact division of labor: Einstein's
causality selects the quantum rule; the quantum amplitude is bought only
by joint resolution; and the precedence structure that joint resolution
requires is precisely what the selected statistics forever hide. What
remains open is stated as precisely: a mechanical realization of the
asymmetry parameter (C3-B-mech), the structural theorem behind the seam
trilemma (the class-M theorem, proved; N-event generalization = C4 G-T),
and the ground-state problem of the stiff chain --- walls mapped, kill
criteria attached, commits public.
\end{quote}

\begin{quote}
A fourth cycle extended the bridge to N parties. A value theorem at N=3:
Mermin M₃ \textgreater{} 2 is achievable in class M iff at least one
space-like pair is ordered --- a single ordered pair suffices for the
algebraic maximum. The tripartite mirror of the bipartite picture is
complete: internal geometry (a shared parity invariant --- the ribbon's
Z₂ holonomy) yields the GHZ signature at the Mermin settings while
capped at the classical bound (the tripartite seam, registered at prior
0.45 before the battery), and one ordered pair crosses it, reproducing
the complete GHZ signature at those settings. The currency of genuine
N-partite nonlocality is binary in block size: disjoint ordered pairs
cap the Mermin-Klyshko value at the 2-producible ceiling for N ≥ 4 and
at the Svetlichny bound, while only a full precedence block attains the
top tier --- algebraic (4.0 at N = 4), above the quantum
2\^{}\{(N−1)/2\}. What cuts class M from the algebraic to the quantum
tier at N parties --- the bipartite answer was no-signaling plus
steering structure --- is the program's registered next open problem.
Schedule-invisibility within a precedence structure stands as a theorem:
the achieved tier certifies the structure; no statistic reveals the
schedule. This cycle's registered retractions (a k-pair ``climbing
ladder'', an over-scoped GHZ claim, a ``45°-tail'' construction) are
part of the public record, per the method frame of §2.
\end{quote}

\subsection{Appendix A --- batteries
(reproducible)}\label{appendix-a-batteries-reproducible}

{\def\LTcaptype{none} % do not increment counter
\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}
  >{\raggedright\arraybackslash}p{(\linewidth - 6\tabcolsep) * \real{0.2500}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Battery
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Prereg
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Raw
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Result
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
C3-B B1--B7 & dd7a74e & 968aaa5 & steering generated, p=2 forced \\
C3-B hardening T1--T3 & 96a3178 & c152c98 & internal derivation
(T1\(\checkmark\)T2\(\checkmark\)) \\
L3 scan + bridge & 2d78c51 & 9567ddb & tail Δ\textgreater0; internal
S(2)=√2 \\
C3-L L1/L2 & 0b10f5d,100a261 & 1e0cf0a,49e8c1b & foliation invisible;
frame-local→ceiling \\
C3-S J1--J7 & 3d516d4 & 324f097 & seam not closed (S-F1/S-F2) \\
S-F3 analytics & --- & 2053106 & closed pre-battery (telegraph) \\
β-coin (class M) & C3L\_coin\_prereg & c8e1bf3 & frameless 2√2,
invisible \\
Class-M theorem & --- & c8e1bf3 & achievability iff shared invisible
precedence \\
C3-B-mech M0 (calibration) & C3Bmech addenda & 0a6c51e & source
polarizes; χ(h) linear \\
C3-B-mech M1/M2 & 63456cd & 2080bbe & mechanical steering, form-free
(M1\(\checkmark\)M2\(\checkmark\)) \\
\end{longtable}
}

\subsection{References}\label{references}

{[}B64{]} J. S. Bell, Physics 1, 195 (1964). {[}CHSH69{]} J. F. Clauser,
M. A. Horne, A. Shimony, R. A. Holt, Phys. Rev.~Lett. 23, 880 (1969).
{[}C80{]} B. S. Cirel'son, Lett. Math. Phys. 4, 93 (1980). {[}CDP11{]}
G. Chiribella, G. M. D'Ariano, P. Perinotti, Phys. Rev.~A 84, 012311
(2011). {[}H92{]} L. Hardy, Phys. Rev.~Lett. 68, 2981 (1992). {[}SS97{]}
A. Suarez, V. Scarani, Phys. Lett. A 232, 9--14 (1997). {[}ZBGT01{]} H.
Zbinden, J. Brendel, N. Gisin, W. Tittel, Phys. Rev.~A 63, 022111
(2001). {[}SZGS02{]} A. Stefanov, H. Zbinden, N. Gisin, A. Suarez, Phys.
Rev.~Lett. 88, 120404 (2002). {[}DGZ92{]} D. Dürr, S. Goldstein, N.
Zanghì, J. Stat. Phys. 67, 843 (1992). {[}Paw09{]} M. Pawłowski et al.,
Nature 461, 1101 (2009). {[}BPA12{]} J.-D. Bancal, S. Pironio, A. Acín,
Y.-C. Liang, V. Scarani, N. Gisin, Nature Phys. 8, 867 (2012).
{[}PR94{]} S. Popescu, D. Rohrlich, Found. Phys. 24, 379 (1994).
{[}G89{]} N. Gisin, Helv. Phys. Acta 62, 363 (1989). {[}G90{]} N. Gisin,
Phys. Lett. A 143, 1 (1990), DOI 10.1016/0375-9601(90)90786-N. {[}G91{]}
N. Gisin, Phys. Lett. A 154, 201 (1991). {[}P91{]} J. Polchinski, Phys.
Rev.~Lett. 66, 397 (1991). {[}S35{]} E. Schrödinger, Proc. Camb. Phil.
Soc. 31, 555 (1935); 32, 446 (1936). {[}HJW93{]} L. P. Hughston, R.
Jozsa, W. K. Wootters, Phys. Lett. A 183, 14 (1993). {[}SBG01{]} C.
Simon, V. Bužek, N. Gisin, Phys. Rev.~Lett. 87, 170405 (2001). {[}A04{]}
S. Aaronson, quant-ph/0401062 (2004).

\end{document}
